The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Edited working directory for consistency

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: html_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/DataAnalysis/')

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
author: "Sam Dundon and Thierry Racaud"
date: "October 24, 2014"
output: html_document
bibliography: Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/Assign2Education/')
